\section{Non functional requirements}
\label{sec:non-func}
\madeby{\jb}{\mb}
This section provides a list of non-functional requirements we have derived based on the description of the Toll system combined with some assumptions about the business case for creating the Toll System.
The system contains three tiers: Toll lanes, toll stations and a enterprise tier. 

\subsection{Toll lane}
Each toll lane consist of a number of hardware components based on which type of toll lane it is.

\subsubsection*{All lanes}
All lanes consists of the following hardware components:

\begin{itemize}
\item A toll lane computer
\item A barrier
\end{itemize}

\subsubsection*{Check-in Lane}
A normal check-in lane must have the following hardware components:

\begin{itemize}
\item Touchscreen for drivers to interact with the system
\item A cash register for accepting cash payments
\item A ticket printer
\item A credit card reader for accepting credit card payments
\end{itemize}

\subsubsection*{Check-out Lane}
A normal check-out lane must have the following hardware components.

\begin{itemize}
\item Ticket reader to validate check-outs
\end{itemize}

\subsubsection*{Express Lane}
An express lane must have the following components.

\begin{itemize}
\item An Antenna to wirelessly read toll tags
\end{itemize}

\subsection{Toll station}
Each toll station consists of a number of check-in and check-out lanes. These are either express lanes or normal lanes.

\subsection{Enterprise}
The enterprise consists of a number of toll stations which are connected to the enterprise. The enterprise server is connected to the internet via a web server.

