\begin{usecase}

\addtitle{Use Case:}{Credit card or cash check-in} 

%Scope: the system under design
%\addfield{Scope:}{System-wide}

%Level: "user-goal" or "subfunction"
\addfield{Description:}{A driver wants to check-in with his vehicle by buying a ticket with credit card or cash.}

%Primary Actor: Calls on the system to deliver its services.
\addfield{Actor:}{Driver, Cashier}

%Stakeholders and Interests: Who cares about this use case and what do they want?
%\additemizedfield{Stakeholders and Interests:}{
%	\item Stakeholder 1 name: his interests
%	\item Stakeholder 2 name: his interests
%}

%Preconditions: What must be true on start and worth telling the reader?
\addfield{Preconditions:}{The driver is at the point of sale at a normal check-in lane.}
%when multiple
%\additemizedfield{Preconditions:}{} 

%Main Success Scenario: A typical, unconditional happy path scenario of success.
\addscenario{Main Scenario:}{
	\item The driver presses the button on the touch screen corresponding to the type of vehicle he drives.
	\item The driver is informed about ticket price on the screen.
	\item The driver uses his credit card to pay for the ticket.
	\item The driver receives his ticket from the ticket printer after the payment has been accepted.
	\item The toll lane barrier is opened.
}

%Extensions: Alternate scenarios of success or failure.
\addscenario{Alternative Scenario:}{
	\item[1.b] The driver is at the point of sale at a normal check-in lane with a cashier present:
		\begin{enumerate}
		\item [1.] The driver requests a ticket from the cashier, providing vehicle information.
		\item [2.] The cashier enters information about the vehicle into the toll lane system.
		\item [3.] The cashier informs the driver about the price.
		\item [4.] The driver pays the cashier.
		\item [5.] The driver takes his ticket from the ticket printer.
		\item [6.] The toll lane barrier is opened.
		\end{enumerate}
	\item[3.a] The credit card payment fails:
		\begin{enumerate}
		\item[1.] If not present, a cashier is summoned to handle the error.
		\item[2.] If error is not resolvable, go to use case ''Cash check-in'', otherwise, go to main scenario step 3.
		\end{enumerate}
	\item [3.a] The driver decides not to buy a ticket
		\begin{enumerate}
		\item[1.] The driver exits the lane without getting on the motorway.
		\end{enumerate}
}

%Special Requirements: Related non-functional requirements.
%\additemizedfield{Special Requirements:}{
%	\item first applicable non-functional requirement
%	\item second applicable non-functional requirement
%}

%Postconditions: What must be true on successful completion and worth telling the reader
\addfield{Postconditions:}{The driver has entered the motorway with a ticket that is valid for 24 hours.}
%when multiple
%\additemizedfield{Preconditions:}{}


%Frequency of Occurrence: Influences investigation, testing and timing of implementation.
%\addfield{Notes:}{}

%Miscellaneous: Such as open issues/questions
%\addfield{Open Issues:}{}

\end{usecase}