\begin{usecase}

\addtitle{Use Case:}{Generate Reports\madeby{\mb}{\kj}} 

%Scope: the system under design
%\addfield{Scope:}{System-wide}

%Level: "user-goal" or "subfunction"
\addfield{Description:}{An Enterprise Manager wants to generate reports with statistics on, types of vehicles that have made check-in/check-out, single ticket usages, toll tag usages in a freely definable time period.}

%Primary Actor: Calls on the system to deliver its services.
\addfield{Actor:}{Enterprise Manager}

%Stakeholders and Interests: Who cares about this use case and what do they want?
%\additemizedfield{Stakeholders and Interests:}{
%	\item Stakeholder 1 name: his interests
%	\item Stakeholder 2 name: his interests
%}

%Preconditions: What must be true on start and worth telling the reader?
\addfield{Preconditions:}{The Enterprise Manager is logged on the enterprise client.}
%when multiple
%\additemizedfield{Preconditions:}{} 

%Main Success Scenario: A typical, unconditional happy path scenario of success.
\addscenario{Main Scenario:}{
	\item The Enterprise Manager query a report in a given time period.
	\item The Enterprise client gathers information for the report from station clients.
	\item The Enterprise Manager can see the report on his/her computer screen.
}

%Extensions: Alternate scenarios of success or failure.
\addscenario{Alternative Scenario:}{
	\item[2.a] Connection fail to Station clients while requesting query from all Station Servers.:
		\begin{enumerate}
		\item[1.] The Enterprise Manager query a report in a given time period.
		\item[2.] The Enterprise Manager can see the report on his/her computer screen, the report dose not include data from Station Servers that could not be reached.
		\item[3.] The Enterprise Manager can see on his/her computer screen which Station Server that where not included in the statistics. 
		\end{enumerate}
}

%Special Requirements: Related non-functional requirements.
%\additemizedfield{Special Requirements:}{
%	\item first applicable non-functional requirement
%	\item second applicable non-functional requirement
%}

%Postconditions: What must be true on successful completion and worth telling the reader
\addfield{Postconditions:}{}
%when multiple
%\additemizedfield{Preconditions:}{}


%Frequency of Occurrence: Influences investigation, testing and timing of implementation.
%\addfield{Notes:}{}

%Miscellaneous: Such as open issues/questions
%\addfield{Open Issues:}{}

\end{usecase}