\section{Non-functional Requirements}
This section provides a list of non-functional requirements we have derived based on the description of the game combined with some assumptions about the business case for creating the game.
\begin{description}

\item [Availability] \hfill 
	\begin{description}
		\item[Working days (Monday - Thursday)] The system should be available 100.0\% of the time between 08:00 AM to 04:00. The system should be available 95\% of the time between 04:00 AM and 08:00 AM in order for updates to be rolled onto the server.
		\item[Weekends (Friday - Sunday)] The system should be available 100.0\% of the time at any time during the day. 
	\end{description}

\item [Restartability] \hfill 
	\begin{itemize}
	   \item The system should be able to restart from a crash in at most 2 minutes, and an average of at most 1 minute.
	\end{itemize}

\item [Portability] \hfill 
	\begin{itemize}
		\item The server side software must be able to run on Linux and Windows servers.
		\item The client side must be able to run on any smartphone OS.
		\item It must be possible to port the game to 95 \% of new OS's within two weeks of work.
	\end{itemize}

\item [Maintainability] \hfill 
	\begin{itemize}
	  	\item A programmer with 1 year of experience must be able to fix 90 \% of confirmed bugs in 5 hours.
	\end{itemize}



\item [Privacy] \hfill 
	\begin{itemize}
		\item Only the player himself as well as administrators are able to see the player profile info after being authenticated in the system.
	\end{itemize}

\item [Usability] \hfill 
	\begin{itemize}
		\item An experienced player should be able to perform any feature on a average time of 30 seconds. 
		\item A player with no prior experience must be able to play the game with all features (chatting, trading, object manipulation and movement) within 15 minutes.
	\end{itemize}

\item[Security] \hfill 
	\begin{itemize}
		\item All player input is validated before processing, in order to avoid e.g. SQL injection.
		\item A player has to authenticate himself before being able to join a game. 
	\end{itemize}

 

\item[Installability] \hfill 
	\begin{itemize}
	     \item Initial installation for the end-user should at most take 15 minutes. 
	     \item Updates for the game is notified to the end-user through notification when the app is started, and the user will be required to download any updates before he can use the game.
	     \item It must be possible to set-up the game server for a person with 1 years of experience within 1 hour of work. 
	     \item A person with 1 year of experience must be able to set up a game with all necessary parameters within 15 minutes. 
	\end{itemize}

 
\end{description}
